Generate data for multispecies modeling, including diet!

### 2020-09-15 NOBAmsdiets.Rmd
refer to archived file

NOBAom <- om_init(here("config/NOBA2config.R")) #run and saved June 19,
# run again 3 August to update biomass_eaten

#NOBAom_ms <- om_species(sppsubset$Name, NOBAom) #run and saved June 19
# run again 3 August to test new wrapper that should save biomass_eaten
NOBAom_ms <- om_species(sppsubset$Name, NOBAom, diet=TRUE)

@@

codbioeaten <- NOBAom_ms$truebioeaten_ss %>%
  filter(species=="North_atl_cod")

>>>>

NOBAom <- om_init(here("config/NOBA2config.R")) #run and saved June 19,
# run again 3 August to update biomass_eaten 
# and output archived with _bio_eaten suffix
# run again 15 Sept to get rid of biomass_eaten

#NOBAom_ms <- om_species(sppsubset$Name, NOBAom) #run and saved June 19
# run again 3 August to test new wrapper that should save biomass_eaten
#NOBAom_ms <- om_species(sppsubset$Name, NOBAom, diet=TRUE)
# and output archived with _bio_eaten suffix
# run again 15 Sept to get rid of biomass eaten
NOBAom_ms <- om_species(sppsubset$Name, NOBAom)

@@

NOBAom_ms_be <- readRDS(file.path(d.name, paste0(scenario.name, "omlist_ss_bio_eaten.rds")))

codbioeaten <- NOBAom_ms_be$truebioeaten_ss %>%
  filter(species=="North_atl_cod")
